% Your fancy acks here. Keep in mind you need to ack each paper you
% use. See the examples here. In addition, each chapter ack needs to
% be repeated at the end of the relevant chapter.
\begin{acknowledgements}

First and foremost, thanks to my parents. Throughout the past six years, being
close to home was a great source of comfort. I love you both, and could not
have asked for better parents.

I would like to acknowledge Professor Amin Vahdat for his support as the chair
of my committee, and for his advice and patience throughout this whole
process.

I would also like to acknowledge George Porter, whose herculean efforts in
co-authorship, cluster management, grant writing and advising have helped
both myself and so many others.

This dissertation would not have been possible without the hard work and
support of my co-authors, whose contributions I would like to acknowledge
individually. Mike Conley was heavily involved in both the TritonSort and
Themis efforts, and wrote Themis' constraint-based memory management system and
the current record-setting MinuteSort implementation. His determination and
enthusiasm were valuable beyond expression.  Harsha Madhyastha was involved
from the earliest days of the TritonSort effort, and was present for the first
successful sort. Radhika Niranjan Mysore put a lot of work into the initial
Heaper-Merger version of the TritonSort architecture, and contributed
significantly to MinuteSort. Alexander Pucher wrote the first iteration of our
radix sort code, and helped me write what would become the final version of
TritonSort in a single, crazed 48-hour push. Rishi Kapoor handled the mammoth
port of CloudBurst to Themis with exceptional graciousness and tenacity. Terry
Lam wrote Themis' PageRank implementation and input generators, and served as
our first real user, helping to make Themis more robust.

Most computer science departments dream of having a system administrator as
deeply knowledgeable, accommodating, and hospitable as Brian Kantor. Thank you
for fighting the never-ending battle against entropy and keeping everything
running through innumerable deadlines.

Chris Nyberg, Mehul Shah and Naga Govindaraju provided conscientious and
patient shepherding of TritonSort through the sort benchmark validation
process. Thanks for keeping us honest and giving us a target to hit. I never
got to meet Jim Gray, but the sort benchmark that he pioneered has had a
profound impact on this phase of my life.

Joe Hellerstein gave me the exposure to computer science research that
convinced me to go to graduate school, the recommendation letter that helped
get me in, and the startup opportunity that got me out. Along the way, he
provided feedback on papers and a great deal of valuable advice.

The work in this dissertation was funded by the National Science Foundation and
generous donations from Cisco and NetApp. Special thanks to Landon Curt Noll
for being our advocate inside Cisco for so many years.

I have been fortunate to make many new friends while at UCSD, and to keep in
touch with friends from Berkeley, Monrovia High and before. Thanking each of
you properly would double the length of this dissertation. You are all
wonderful people, and I couldn't have finished this without you. I am so
incredibly fortunate to have all of you in my life.

\input{tritonsort_ack}

\input{themis_ack}

\input{themis-ft_ack}

\end{acknowledgements}
