\documentclass[10pt]{article}
\usepackage{../externals/ucsddissertation/permission/ucsdcseletterhead}
\usepackage{parskip}
\usepackage[margin=1in]{geometry}
\usepackage{mathptmx}
\usepackage{courier}
\usepackage[scaled=.92]{helvet}
\usepackage[T1]{fontenc}
\pagestyle{empty}
\begin{document}
\hfill\today

Kim Barrett, Dean\\
Graduate Studies\\
402 University Center, 0003\\
UC San Diego\\
La Jolla, CA 92093-0003

\vskip\baselineskip
Dear Dean Barrett:

We request permission for Alexander Rasmussen to use the following publications
in his doctoral dissertation. Mr.\ Rasmussen was the principle
researcher/author on these papers.

Rasmussen, Alexander; Porter, George; Conley,
Michael; Madhyastha, Harsha; Niranjan Mysore, Radhika; Pucher, Alexander;
Vahdat, Amin. ``TritonSort: A Balanced Large-Scale Sorting System,'' USENIX
Symposium on Networked Systems Design and Implementation, April 2011.

Rasmussen, Alexander; Conley, Michael; Kapoor, Rishi; Lam, Vinh
The; Porter, George; Vahdat, Amin. ``Themis: An I/O-Efficient MapReduce,'' ACM
Symposium on Cloud Computing, October 2012.

We further request permission for Alexander Rasmussen to use material that has
been submitted for publication. Mr.\ Rasmussen was the principal
researcher/author on this paper.

Rasmussen, Alexander; Porter, George; Vahdat, Amin. ``I/O-Efficient Fault
Tolerance for MapReduce.''

\vskip3\baselineskip
\parbox[t]{.5\textwidth}{%
Professor Amin Vahdat\\
Chair of Committee}%
\parbox[t]{.5\textwidth}{%
Alexander Rasmussen}
\end{document}
